\chapter{SAN iSCSI CSI}

% Une partie destinée à convaincre un supérieur hiérarchique de reprendre la responsabilité complète du projet sur lequel vous avez travaillé pendant votre stage. Vous mettrez en avant vos atouts pour une telle mission en justifiant vos capacités.

The following document is an email sent to my manager to ask him for the full responsibility over the SAN iSCSI CSI project.

\clearpage

\mail{Proposal to take the lead on SAN iSCSI CSI}{
    I address you this e-mail today because I would like to take the lead on our project SAN iSCSI CSI. I currently already have the lead on the development part but I think I could entierly endorse the role of project leader.

    Through my two internships at Enix, I acquired a lot of experience around the project SAN iSCSI CSI. After one year working on it, I understood many of its ins and outs and I had to work on each parts of the plugin, releasing 3 major versions and improving it in many ways. In a sense, I acquired a certain expertise on the subject. I have a quite good understanding around tools like multipathd, iSCSI, Kubernetes, the CSI specification and many others.

    I'm also very able to take decisions and initiatives. I already did sometimes, for instance with the refactor of the logging system, allowing to debug more easily the plugin. Or with the setup of a Prometheus exporter, allowing to export statistics to a Grafana dashboard and thus making us able to monitor the well functioning of the plugin.

    I also understand marketing and public relations quite well. I participated to a few meetings with the Seagate team developping the next generation of their appliances. I take this opportunity to remind that this partnership started with a reply to one of my tweet by John Suykerbuyk (Staff Software Engineer at Seagate Technology) \source{\href{https://twitter.com/johnsuykerbuyk/status/1369287724859990019}{Twitter}}.

    For those reasons, I think it could be a great opportunity for Enix, but also for me, to let me take the lead on this project. I can get SAN iSCSI CSI to meet Enix's expectations while taking even more experience through the process of project management, which will eventually become handy for Enix when I will be working on other projects.

    Thanks you by advance for considering my offer, I'm sure you will have a enlightened thought about it.
}

\clearpage
